Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
minor rewordings

The question was also posed as to whether the distinction between researcher
and developer is sensible, with James Hetherington commenting that in the UK
a more nuanced view of research software engineers
and researcher developers is examined. Should this be less of a contract relationship, and
more of a collaborative relationship. This is also at the core of the business
model that Kitware presented in its submission to the workshop. Are other
ingredients missing such as applied mathematicians? Should this be defined more
in terms of skill sets rather than roles and/or identities? This builds on the
comments from Vaidy Sunderam that scientists are generally good writers, and
have mathematical skills, so why can't they learn software engineering
principles?

Miller commented that all of the infrastructure that sits around a new
algorithm that we need to make it useful and sustainable requires different
skill sets than the algorithm developer. Friere commented that there are no
good career paths for people with broad skills, no incentives for them to
continue in these roles. There was debate around people doing what interests
them, and learning computing leaves people cold, but is it that it leaves the
people who find career paths in academia cold versus the full spectrum of
people involved in research? Is this also caused by poor teaching, or that the
perceived benefits for doing this are too small? It could also be attributed to
their focus being on science, not software engineering, or do the people with
the passion for software engineering in science simply have no viable career
path and either adapt or seek out alternate career paths.

>>>>

The question was also posed as to whether the distinction between researcher
and developer is sensible, with James Hetherington commenting that in the UK
a more nuanced view of research software engineers
and researcher developers is examined. Should this be less of a contract relationship, and
more of a collaborative relationship? This is also at the core of the business
model that Kitware presented in its submission to the workshop. Are other
ingredients missing such as applied mathematicians? Should this be defined more
in terms of skill sets rather than roles and/or identities? This builds on the
comments from Vaidy Sunderam that scientists are generally good writers, and
have mathematical skills, so why can't they learn software engineering
principles?

Miller commented that all of the infrastructure that sits around a new
algorithm that we need to make it useful and sustainable requires different
skill sets than the algorithm developer. Friere commented that there are no
good career paths for people with broad skills, no incentives for them to
continue in these roles. There was debate around people doing what interests
them, and learning computing leaves people cold, but is it that it leaves the
people who find career paths in academia cold versus the full spectrum of
people involved in research? Is this also caused by poor teaching, or because the
benefits for doing this are perceived as too small? It could also be attributed to
their focus being on science, not software engineering, or do people with
the passion for software engineering in science simply have no viable career
path and either adapt or seek out alternate career paths?
